### 2020-07-03 introduction.tex
more editing

This thesis demonstrates latest capabilities of Moltres
\cite{lindsay_introduction_2018}, an open source MSR simulation tool. Moltres
is an application built in the \gls{MOOSE} parallel finite element framework.
It solves
the deterministic multigroup neutron diffusion and thermal-hydraulics
\glspl{PDE} simultaneously on the same mesh. It supports up to 3-D meshes and
scales well for a large number of processors. The underlying \gls{MOOSE}
framework
provides a range of implicit and explicit methods for the coupling between the
neutronics and thermal-hydraulics governing equations.

In the introductory journal article for Moltres, Lindsay et al.
\cite{lindsay_introduction_2018} demonstrated Moltres' capabilities with
2D-axisymmetric and 3D models of the \gls{MSRE}. The results showed good
qualitative agreement with legacy \gls{MSRE} data but there were some minor
quantitative discrepancies due to a number of differences in the legacy model. 
Moltres has undergone further development in the past two years. The authors
from the first paper have since developed various new capabilities in Moltres
such as support for looping delayed neutron precursors back into the core,
and a heat exchanger object to set the heat removal rate.

In addition to those new capabilities, this thesis presents two more recent
developments in Moltres, namely fully integrating \gls{MOOSE}'s incompressible
Navier-Stokes module into Moltres, and introducing a
decay heat model. The incompressible Navier-Stokes module provides a more
accurate representation of the flow profile, precursor movement, and heat
transfer as opposed to assuming uniform or function-based velocity fields.

@@

The main objectives of this thesis are to demonstrate and verify Moltres'
latest capabilities in modeling multiphysics, steady-state, and transient
behavior of fast-spectrum \glspl{MSR} through the study of the \gls{MSFR}
concept. Code-to-code verification is an important exercise in software
development for ensuring that the application produces accurate and reliable
results. This thesis covers the \gls{MSFR} concept mainly because 
there is readily available literature data to verify our results against. The
steady-state and transient results also feature a significant degree of
physics interaction between the neutronics and thermal-hydraulics. This
present work will first present a verification of Moltres' \gls{MSFR}
neutronics results against Serpent 2, followed by a verification of
the coupled neutronics/thermal-hydraulics steady-state and transient accident
results against results from the Polimi and TUDelft models published by
Fiorina et al. \cite{fiorina_modelling_2014}. The
secondary objective is to identify areas of improvement in Moltres for future
research.

@@

The outline of this thesis is as follows. Chapter 2 discusses the history and
features of \glspl{MSR}, and a literature review of existing \gls{MSR}
simulation tools. The chapter also covers the \gls{MSFR} concept in greater
detail. Chapter 3 details the simulation codes and the general modeling
approach for generating the results in this thesis. Chapter 4 provides a
neutronics assessment by comparing key neutronics parameters from Moltres'
eigenvalue calculations to Serpent's Monte Carlo calculations. Chapter 5
presents steady-state results of coupled neutronics/thermal-hydraulics
\gls{MSFR} simulations in Moltres. Chapter 6 presents transient accident
simulation results for unprotected reactivity insertions, unprotected loss of
heat sink, unprotected loss of flow, and unprotected pump overspeed,
respectively. Lastly, Chapter 7 summarizes the key findings in this thesis
and posits some potential avenues for future work.

>>>>

Moltres is an open source MSR simulation tool that falls under the latter
category \cite{lindsay_introduction_2018}. It is an application built in the
\gls{MOOSE} \cite{gaston_physics-based_2015} parallel finite element
framework. Lindsay et al. first presented the tool in 2017 and demonstrated
its capabilities by simulating 2-D and 3-D models of the \gls{MSRE}
\cite{lindsay_introduction_2018}. The results showed good qualitative
agreement with the original design calculations by \gls{MSRE} researchers at
\gls{ORNL}. There has since been new developments in Moltres allowing for
more accurate \gls{MSR} simulations.

@@

This thesis demonstrates latest capabilities of Moltres
\cite{lindsay_introduction_2018}, an open source MSR simulation tool.
In particular, this thesis presents two more recent
developments in Moltres, namely fully integrating \gls{MOOSE}'s incompressible
Navier-Stokes module into Moltres, and introducing a
decay heat model.
The main objective of this thesis is to verify Moltres'
latest capabilities in modeling multiphysics, steady-state, and transient
behavior of fast-spectrum \glspl{MSR} through the study of the \gls{MSFR}
concept. Code-to-code verification is an important exercise in software
development for ensuring that the application produces accurate and reliable
results. This thesis covers the \gls{MSFR} concept mainly because 
there is readily available literature data to verify our results against. The
steady-state and transient results also feature a significant degree of
physics interaction between the neutronics and thermal-hydraulics. This
present work will first present a verification of Moltres' \gls{MSFR}
neutronics results against Serpent 2, followed by a verification of
the coupled neutronics/thermal-hydraulics steady-state and transient accident
results against results from the Polimi and TUDelft models published by
Fiorina et al. \cite{fiorina_modelling_2014}. The
secondary objective is to identify areas of improvement in Moltres for future
research.

@@

The outline of this thesis is as follows. Chapter 2 discusses the history and
features of \glspl{MSR}, and a literature review of existing \gls{MSR}
simulation tools. The chapter also covers the \gls{MSFR} concept in greater
detail. Chapter 3 details the software and the general modeling
approach for generating the results in this thesis. Chapter 4 provides a
neutronics assessment by comparing key neutronics parameters from Moltres'
eigenvalue calculations to Serpent's Monte Carlo calculations. Chapter 5
presents steady-state results of coupled neutronics/thermal-hydraulics
\gls{MSFR} simulations in Moltres. Chapter 6 presents transient accident
simulation results for unprotected reactivity insertions, unprotected loss of
heat sink, unprotected loss of flow, and unprotected pump overspeed,
respectively. Lastly, Chapter 7 summarizes the key findings in this thesis
and posits some potential avenues for future work.
